\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning on Unsecured Trajectories

### 2023-09-14 paper.tex
update

\begin{definition}\label{sec:ellipsoidal definition}
	The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the workspace such that there exist a trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$.
\end{definition}
This region can be analytically bounded via an ellipsoid:
\begin{definition}\label{def:Reachability}
	The \emph{reachability ellipsoid} is defined as the region  $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q}+q_2)<2a\}$, where $a=\frac{v_{maq}}{2}(t_2-t_1)$.
\end{definition}

@@

\subsubsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
To simplify the problem, we employ a canonical rigid body transformation that repositions the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$. In this new frame, the ellipsoid's center aligns with the origin, and its foci align with the first axis of $\cF_\cE$. We perform this transformation in a differentiable manner, with respect to the two foci serving as waypoints for a robot.

For the convenience of derivation, we define the coordinate transformation from $\cF$ to $\cF_\cE$ using a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$, which, to simplify the notation, we simply refer to as $R$ and $o$, respectively. The transformation of a point from the frame $\cF_\cE$ to the frame $\cF$ and its inverse are given by the formulation:
  \begin{equation}
    \Fframe{q}=R\Eframe{q}+o,\label{eq:E to F transform}\quad
    \Eframe{q}=R\transpose(\Fframe{q}-o).
  \end{equation}

  We define $\nu_\cF$ and $\nu_\cE$ to represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. Formally:
  \begin{align}
    \nu'_\cF&=q_2-q_1, & \nu_\cF &= \frac{\nu'_\cF}{\norm{\nu_\cF}}, & \nu_\cE&=[1,0,0]^T;
  \end{align}
  see Fig.\ref{fig:EllipseConstraintExample} for an illustration. Note that $\nu_\cE$ is constant while, for the sake of clarity, $\nu_{\cF}$ depends on $q_1,q_2$. We then define the rotation $R$ using a \emph{Householder rotation}, while from \eqref{eq:E to F transform} we see that $o$ represents the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:
  \begin{align} 
    R&=H(\nu_\cF(q_1,q_2),\nu_\cE(q_1,q_2)), &o&=\frac{1}{2}(q_1+q_2).
  \end{align}
  In the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. 
  The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, where the coordinates of the two foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ are
  \begin{align}
    q^\cE_1=\bmat{c & 0 & 0}\transpose, && q^\cE_2=\bmat{-c & 0 & 0}\transpose,
  \end{align}
  with $c=\frac{\norm{q_2-q_1}}{2}$.
\begin{definition}
  The ellipsoid $\cE$ in the canonical frame can be described as the zero level set of the quadratic function
  \begin{equation}\label{equ:standard-ellipse}
    \Eframe{E}(\Eframe{q}) = \Eframe{q}\transpose Q \Eframe{q} - 1
  \end{equation}
  where
  \begin{equation}
    Q = \diag(a^{-2},b^{-2},b^{-2}),
  \end{equation}
  and $b = \sqrt{a^2-c^2}$.
  The ellipse parameters $a$,$b$ represent the lengths of the major axes.
  And the original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
   \begin{equation}
     \Fframe{E}(\Fframe{q}) = (\Fframe{q}-o_\cE)\transpose H\transpose Q H (\Fframe{q}-o_\cE) - 1
     \end{equation}
\end{definition}

For all reachability ellipsoid constraints, we first solve the problem in the canonical frame $\cF_{\cE}$, and transform the solutions to the global frame $\cF$ using the defined transformation function.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\linewidth, trim = 0cm 1.5cm 0cm 1cm, clip]{Ellipse2line_V2}
\caption{Plane-ellipse constraint. Projected a ellipsoid to one side of a plane. The projection is simplified to the point-ellipse constraint as projecting a point inside ellipse $p_{L}$ to $p_{t}$ on outside the ellipse.}
\label{fig:Ellipse-to-plane}
\end{center}
\end{figure}

For forbidden region in the shape of a hyperplane $\mathcal{L}(\tilde{q}) = \{\tilde{q}\in\mathbb{R}^n: \vn\transpose \tilde{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}). The reachability constraint now can then be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$. When transformed into canonical frame, the hyperplane can be written as $\Eframe \cL(\tilde{q}) = \{  \tilde{q}\in\mathbb{R}^m:  \vn_\cE\transpose \tilde{q} = d_{\cE}\}$, where,
  \begin{equation}
    n_\cE = H(q_1,q_2)n, \quad d_\cE =-\vn\transpose o + d
\end{equation}
The corresponding constraint can be written as:

\begin{constraint}[Plane-ellipsoid reachability constraint]
\begin{align}
D(\vq) &= H^{-1}(q(t_1),q(t_2))\pi^\cE_{\vn \cE}(q)+o, \label{eq:plane_ellipsoid_constraint}\\
  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_{\vn}(q)} = 0 \},\\
   \Pi_\sZ(z) & = \overrightarrow{0}, 
\end{align}
\end{constraint}
where $\pi^\cE_{\vn \cE}(q)$ is the projection operator defined as:
  \begin{equation}\label{equ:plane2ellipse}
    \pi^\cE_{\vn \cE}(q) =\begin{cases}
      p^\cE_{t1}-p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
      p^\cE_{t2}-p^\cE_{\cL} &  d_\cE \in [- d_{\cE t},0), \\
      {0} & \textrm{otherwise}.
    \end{cases}
  \end{equation}
$p^{\cE}_{1}$ and $p^{\cE}_{2}$ are tangent points on two planes $\Eframe \cL_{1} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} =  d_{\cE t} \}$ and $\Eframe \cL_{2} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} = - d_{\cE t} \}$ that are parallel to $\cL$ and tangent to the ellipse (\Cref{fig:Ellipse-to-plane}), defined as 
 \begin{equation}
    p^\cE_{1} = \frac{ d_{\cE t} Q^{-1}   n_\cE}{ n_\cE \transpose Q^{-1}  n_\cE} = \frac{Q^{-1} n_\cE}{ d_{\cE t}},\quad  p^\cE_{2} = -  p^\cE_{1},
  \end{equation}
where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$. And the \emph{tangent interpolation point} is defined as 
    \begin{equation}\label{equ:ProjectPoint}
      p^\cE_{\cL} = \frac{ d_\cE Q^{-1} n_\cE}{ n_\cE\transpose Q^{-1} n_\cE}.
    \end{equation}
  Note that $p^\cE_{\cL} \in \mathcal{L}$ and when  $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{1}$ or $p^\cE_{\cL}=p^\cE_{2}$, respectively.

  It is clear that when $ d_\cE \in [- d_{\cE t},  d_{\cE t}]$, the plane $\cL$ and the ellipsoid $\cE$ have at least one intersection, thus violating our desired reachability constraint.

  \begin{proposition}\label{prop:dpi_ne_dt}
    The differential of the projection function $\Eframe \pi_{\vn \cE}(q)$ with respect to the foci $q_1$ and $q_2$ is given by:
    \begin{equation}
      \partial_q \pi^\cE_{\vn \cE}(q) = \begin{cases}
        \partial_q p^\cE_{t1}-\partial_q p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
        \partial_q p^\cE_{t2}-\partial_q p^\cE_{\cL} &  d \in [- d_{\cE t},0), \\
        {0} & otherwise.
      \end{cases}
    \end{equation}
    where
    \begin{multline}
      \partial_q p_\cL =   (-\frac{d_{\cE t} n\transpose \partial_q o -2d_\cE \partial_q d_{\cE t}}{d_{\cE t}^3} )Q^{-1}n_\cE \\
      + \frac{d_\cE\partial_b Q^{-1} n_\cE \partial_q b -  2d_\cE Q^{-1}H[n]_\times U}{d_{\cE t}^2},
    \end{multline}
    \begin{equation}
      \partial_q p_{1} =  -\frac{Q^{-1}n_\cE \partial_q d_{\cE t} }{d_{\cE t}^2} 
      + \frac{\partial_b Q^{-1}n_\cE \partial_q b -  2Q^{-1}H[n]_\times U }{d_{\cE t}}.
    \end{equation}
  \end{proposition}
  \begin{proof}
  See \Cref{proof:dpi_ne_dt}.
  \end{proof}
  Based on the previous proposition, the differential of (\ref{eq:plane_ellipsoid_constraint}) can be written as:
  \begin{equation}
    \partial_q {D_{\vn\cE}} = -2 H \cross{\Eframe \Pi_{\vn \cE}}  M + H^{-1}\partial_q \Eframe \Pi_{\vn \cE}
  \end{equation}

@@

For a intermediate step to get the relationship between a polygon shaped forbidden region, the relative position between the ellipse and segment of the hyperplane that defines the region is studied. Assume the segment has endpoints $p_1$ and $p_2$, the segment can be defined as:
\begin{equation}
\bmat{(p_1-p_2)\transpose\\(p_2-p_1)\transpose} p \leq \bmat{p_2\transpose\\-p_1\transpose}(p_1-p_2)
\end{equation}
And using the $p_{\cL}$ defined in (\ref{equ:ProjectPoint}), we define
\begin{equation}
D_{seg}(q) = \begin{cases}
D_1(p_1) & (p_1-p_2)\transpose (p_{\cL}-p_2)<0\\
D_1(p_2) & (p_2-p_1)\transpose (p_{\cL}-p_1)<0\\
D_2(p_{\cL}) & otherwise
\end{cases}
\end{equation}
where $D_{p\cE}$ and $D_{\vn\cE}$ are corresponding constraint function introduced in section \ref{sec:ellipsoid-point} and \ref{sec:ellipsoide-plane}
with the constraint set and projection written as:
\begin{equation}
\zeta_{seg} = \{q\in\mathbb{R}^{nm}:\norm{D_{seg}(q)} = 0 \}
\end{equation}
\begin{equation}
\Pi_{seg}(D_{seg}(q)) = {0}
\end{equation}
\subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint} 
To keep an ellipse away from a convex polygon, first, we need to keep all segments of the hyperplanes outside the ellipse. And a convex obstacle constraint for the polygon (as introduced in section \ref{sec:obstacle}) is also added to prevent cases where the ellipse is a subset of the region. Similar to \eqref{equ:ProjectPoint}, we define
\begin{equation}
D_{cp}(q) = \bmat{D_{seg1}\\D_{seg2}\\ \vdots}
\end{equation}
with the constraint set and projection written as:
\begin{equation}
\zeta_{cp} = \{q\in\mathbb{R}^{nm}:\norm{D_{cp}(q)} = 0 \}
\end{equation}
\begin{equation}
\Pi_{cp}(D_{cp}(q)) = {0}
\end{equation}

@@

Based on the schedule, reachability for agent 1 in-between the scheduled co-observations are constrained. Notice that additional checkpoint (i.e. stationary security camera) need to be incorporated in order to generated an attack-proof solution. Additional solutions to avoid these checkpoints will be discussed in Chapter \ref{chapter:cross-trajectory}.

>>>>

\begin{definition}\label{sec:ellipsoidal definition}
	The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the workspace such that there exist a trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$.
\end{definition}
This region can be analytically bounded via an ellipsoid:
\begin{definition}\label{def:Reachability}
	The \emph{reachability ellipsoid $\cE$} is defined as the region  $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q}+q_2)<2a\}$, where $a=\frac{v_{maq}}{2}(t_2-t_1)$.
\end{definition}

@@

\subsubsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
To simplify the problem, we employ a canonical rigid body transformation that repositions the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$. 
\rtronhl{Make this sentence as "The canonical frame $\cF_\cE$ is defined as..."}{In this new frame, the ellipsoid's center aligns with the origin, and its foci align with the first axis of $\cF_\cE$.} We perform this transformation in a differentiable manner, with respect to the two foci serving as waypoints for a robot.
We parametrize the transformation from $\cF$ to $\cF_\cE$ using a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$, which, to simplify the notation, we refer to as $R$ and $o$, respectively. 
The transformation of a point from the frame $\cF_\cE$ to the frame $\cF$ and its inverse are given by the rigid body transformations:
  \begin{equation}\label{eq:transformations}
    \Fframe{q}=R\Eframe{q}+o,\label{eq:E to F transform}\quad
    \Eframe{q}=R\transpose(\Fframe{q}-o).
  \end{equation}

  We define $\nu_\cF$ and $\nu_\cE$ to represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. Formally:
  \begin{align}
    \nu'_\cF&=q_2-q_1, & \nu_\cF &= \frac{\nu'_\cF}{\norm{\nu_\cF}}, & \nu_\cE&=[1,0,0]^T;
  \end{align}
  see Fig.\ref{fig:EllipseConstraintExample} for an illustration. Note that $\nu_\cE$ is constant while, for the sake of clarity, $\nu_{\cF}$ depends on $q_1,q_2$. From the definition of $\cF_\cE$, the rotation $R$ can be found using a \emph{Householder rotation}, while from \eqref{eq:E to F transform} the translation $o$ must be equal to the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:
  \begin{align} 
    R&=H(\nu_\cF(q_1,q_2),\nu_\cE(q_1,q_2)), &o&=\frac{1}{2}(q_1+q_2).
  \end{align}
  To simplify notation, in the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. 
  The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, where the coordinates of the two foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ are
  \begin{align}
    q^\cE_1=\bmat{c & 0 & 0}\transpose, && q^\cE_2=\bmat{-c & 0 & 0}\transpose,
  \end{align}
  with $c=\frac{\norm{q_2-q_1}}{2}$.
\begin{definition}
  The \emph{reachability ellipsoid $\cE$ in the canonical frame} is defined as as the zero level set of the quadratic function
  \begin{equation}\label{equ:standard-ellipse}
    \Eframe{E}(\Eframe{q}) = \Eframe{q}\transpose Q \Eframe{q} - 1
  \end{equation}
  where
  \begin{equation}
    Q = \diag(a^{-2},b^{-2},b^{-2}),
  \end{equation}
  and $b = \sqrt{a^2-c^2}$.
  The ellipse parameters $a$, $b$ represent the lengths of the major axes.
\end{definition}
\begin{lemma}
The original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
   \begin{equation}\label{eq:ellpsoid from canonical}
     \Fframe{E}(\Fframe{q}) = (\Fframe{q}-o_\cE)\transpose H\transpose Q H (\Fframe{q}-o_\cE) - 1
     \end{equation}
\end{lemma}
\begin{proof}
    The claim follows by substituting  \eqref{eq:transformations} into \eqref{equ:standard-ellipse}, and from the definition of $R$ and $o$.
\end{proof}
For all reachability ellipsoid constraints, we first solve the problem in the canonical frame $\cF_{\cE}$, and transform the solutions to the global frame $\cF$ using the transformation \eqref{eq:transformations}.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\linewidth, trim = 0cm 1.5cm 0cm 1cm, clip]{Ellipse2line_V2}
\rtron{Add $d_{\cE t}$}
\caption{Plane-ellipse constraint. Projected a ellipsoid to one side of a plane. The projection is simplified to the point-ellipse constraint as projecting a point inside ellipse $p_{L}$ to $p_{t}$ on outside the ellipse.}
\label{fig:Ellipse-to-plane}
\end{center}
\end{figure}

For forbidden region in the shape of a hyperplane $\mathcal{L}(\tilde{q}) = \{\tilde{q}\in\mathbb{R}^n: \vn\transpose \tilde{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}). The reachability constraint now can then be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$. When transformed into canonical frame, the hyperplane can be written as $\Eframe \cL(\tilde{q}) = \{  \tilde{q}\in\mathbb{R}^m:  \vn_\cE\transpose \tilde{q} = d_{\cE}\}$, where,
  \begin{equation}
    n_\cE = H(q_1,q_2)n, \quad d_\cE =-\vn\transpose o + d.
\end{equation}
Intuitively, $d_\cE$ can be thought as a distance between the the plane $\cL$ and the origin (i.e., the center of $\cE$.

\rtron{Move the definition of tangents, tangent points, and tangent interpolation point here}

With these definitions, the constraint can be written as:

\begin{constraint}[Plane-ellipsoid reachability constraint]
\begin{align}
D(\vq) &= H^{-1}(q(t_1),q(t_2))\pi^\cE_{\vn_\cE}(q)+o, \label{eq:plane_ellipsoid_constraint}\\
  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_{\vn}(q)} = 0 \},\\
   \Pi_\sZ(z) & = \overrightarrow{0}, 
\end{align}
\end{constraint}
\rtron{Check that $q$ is $\vq$ where necessary. Also sometimes you use $q(t_1),q(t_2)$ and sometimes $q_1,q_2$, check for consistency.}
where $\pi^\cE_{\vn_\cE}(q)$ is the projection operator defined as:
  \begin{equation}\label{equ:plane2ellipse}
    \pi^\cE_{\vn_\cE}(q) =\begin{cases}
      p^\cE_{1}-p^\cE_{\cL} & \textrm{ if } d_\cE \in [0, d_{\cE t}], \\
      p^\cE_{2}-p^\cE_{\cL} &  \textrm{ if } d_\cE \in [- d_{\cE t},0), \\
      {0} & \textrm{otherwise}.
    \end{cases}
  \end{equation}
$p^\cE_1$ and $p^\cE_2$ are tangent points on two planes that are parallel to $\cL$ and tangent to the ellipse, $\cL_1^{\cE} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} =  d_{\cE t} \}$ and $\cL_2^{\cE} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} = - d_{\cE t} \}$  (\Cref{fig:Ellipse-to-plane}). Analytically, these points can be found as 
 \begin{equation}
    p^\cE_{1} = \frac{ d_{\cE t} Q^{-1}   n_\cE}{ n_\cE \transpose Q^{-1}  n_\cE} = \frac{Q^{-1} n_\cE}{ d_{\cE t}},\quad  p^\cE_{2} = -  p^\cE_{1},
  \end{equation}
where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$; intuitively, $d_{\cE t}$ can be thought as a distance between the tangent planes $\cL_1^\cE$, $\cL_2^\cE$ and the origin (i.e., the center of the ellipse $\cE$).
The \emph{tangent interpolation point} $p^\cE_{\cL} \in \mathcal{L}$ is defined on the plane by 
    \begin{equation}\label{equ:ProjectPoint}
      p^\cE_{\cL} = \frac{ d_\cE Q^{-1} n_\cE}{ n_\cE\transpose Q^{-1} n_\cE}.
    \end{equation}
  Intuitively, the point $p^\cE_\cL$ is the point on $\cL$ which is closest to either $p^\cE_1$ or $p^\cE_2$.
  Note that when  $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{1}$ or $p^\cE_{\cL}=p^\cE_{2}$, respectively. When $ d_\cE \in [- d_{\cE t},  d_{\cE t}]$, the plane $\cL$ and the ellipsoid $\cE$ have at least one intersection, thus violating our desired reachability constraint.

  \begin{proposition}\label{prop:dpi_ne_dt}
    The differential of the projection function $\pi^\cE_{\vn \cE}(q)$ with respect to the foci $q_1$ and $q_2$ is given by:
    \begin{equation}
      \partial_q \pi^\cE_{\vn \cE}(q) = \begin{cases}
        \partial_q p^\cE_{t1}-\partial_q p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
        \partial_q p^\cE_{t2}-\partial_q p^\cE_{\cL} &  d \in [- d_{\cE t},0), \\
        {0} & otherwise.
      \end{cases}
    \end{equation}
    where
    \begin{multline}
      \partial_q p_\cL =   (-\frac{d_{\cE t} n\transpose \partial_q o -2d_\cE \partial_q d_{\cE t}}{d_{\cE t}^3} )Q^{-1}n_\cE \\
      + \frac{d_\cE\partial_b Q^{-1} n_\cE \partial_q b -  2d_\cE Q^{-1}H[n]_\times U}{d_{\cE t}^2},
    \end{multline}
    \begin{equation}
      \partial_q p_{1} =  -\frac{Q^{-1}n_\cE \partial_q d_{\cE t} }{d_{\cE t}^2} 
      + \frac{\partial_b Q^{-1}n_\cE \partial_q b -  2Q^{-1}H[n]_\times U }{d_{\cE t}}.
    \end{equation}
  \end{proposition}
  \begin{proof}
  See \Cref{proof:dpi_ne_dt}.
  \end{proof}
  Based on the previous proposition, the differential of (\ref{eq:plane_ellipsoid_constraint}) can be written as:
  \begin{equation}
    \partial_q {D_{\vn\cE}} = -2 H \cross{\Eframe \Pi_{\vn \cE}}  M + H^{-1}\partial_q \Eframe \Pi_{\vn \cE}
  \end{equation}

@@

For a intermediate step to get the relationship between a polygon shaped forbidden region, the relative position between the ellipse and segment of the hyperplane that defines the region is studied. 
Assume the segment has endpoints $p_1$ and $p_2$; then the segment can be defined as:
\begin{equation}
\bmat{(p_1-p_2)\transpose\\(p_2-p_1)\transpose} p \leq \bmat{p_2\transpose\\-p_1\transpose}(p_1-p_2)
\end{equation}
\rtron{Needs an additiona constraint that $p$ needs to be on the line $p_1p_2$.}
\begin{constraint}[Line-segment-ellipsoid reachability constraint]
\begin{align}
D(\vq) &=  \begin{cases}
D_1(p_1) & (p_1-p_2)\transpose (p_{\cL}-p_2)<0\\
D_1(p_2) & (p_2-p_1)\transpose (p_{\cL}-p_1)<0\\
D_2(p_{\cL}) & \textrm{otherwise}
\end{cases} \label{eq:segment_ellipsoid_constraint}\\
  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_p(q)} = 0 \},\\
   \Pi_\sZ(z) & = 0, 
\end{align}
\end{constraint}

\rtron{Define $D_1$, $D_2$. Give intuition about what they represent.}
\subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint} 
To keep an ellipse away from a convex polygon, first, we need to keep all segments of the hyperplanes outside the ellipse. Similar to \eqref{equ:ProjectPoint}, we define
\begin{constraint}[Convex-polygon-ellipsoid reachability constraint]\label{constraint:polygon-ellipsoid}
\begin{align}
D(\vq) &= \bmat{D_{seg1}\\D_{seg2}\\ \vdots} \label{eq:region_ellipsoid_constraint}\\
  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_p(q)} = 0 \},\\
   \Pi_\sZ(z) & = 0, 
\end{align}
\end{constraint}
\rtron{$D_{seg1}, D_{seg2}$ need to be defined.}
ADMM constraint~\ref{constraint:polygon-ellipsoid} needs to be supplemented with a convex obstacle constraint for the polygon (as introduced in section \ref{sec:obstacle}) to prevent cases where the ellipse is a subset of the region.

@@

Based on the schedule, reachability for agent 1 in-between the scheduled co-observations are constrained. Notice that additional checkpoint (i.e. stationary security camera) need to be incorporated in order to generated an attack-proof solution. Additional solutions to avoid these checkpoints will be discussed in \Cref{chapter:cross-trajectory}.
